\documentclass[twocolumn]{dndbook}


\begin{document}

\chapter*{Simply Psionics}

This is psionics system designed to be very easy to play, without any accounting of psi points or complex powers.
It is meant to be a pluggable option, rather than a class.
The inspiration comes from multiple sources:
Eleven from Stranger Things, who has a few simple but powerful abilities,
and the Stephen King novel \emph{Carrie}, and others.
In essence - I do not want to track points, I do not want to create psi-swords or anything of the swoerd.
I just want to play a PC or create an NPC with telepathy, telekinesis, or pyrokinesis in the traditional sense.\par

How psionics fits within the world is up to the DM.
If this is a rare and not-well-known phenomemnon in the campaign setting,
the origin feats described below can be overpowered.
In particular, the hard-to-detect \emph{Mage Hand} ability can pose challenges where players are able to circumvent challenges.\par

\section*{Telekinesis}

Telekinesis is a collection of five feats, and players can take as many as they want.
Choose a spellcasting ability for each feat - Charisma, Intelligence, or Wisdom.
Use it for all of the spell effects granted by that feat.

\subsection{Telekinesis I}
{\emph{Origin Feat}}\par
Whether by mutation, training, or some other means, you have learned to move small objects with your mind.
You gain the following abilities:
\paragraph*{Mage Hand Cantrip} You gain the \emph{Mage Hand} cantrip,
except the hand is invisible and does not require verbal or somatic components.
It is basically undetectable by mundane means,
although \emph{Detect Magic} reveals it.
Your spellcasting ability for this cantrip is Charisma or Wisdom - discuss with the DM.
\paragraph*{Tenser's Floating Desk} You can cast \emph{Tenser's Floating Disk},
without requiring verbal or somatic components.
The disk is invisible and cannot be detected by mundane means,
although \emph{Detect Magic} or similar magic reveals it.
If detected through \emph{True Seeing}, it does not appear as a normal hand, but rather a mass of telekinetic energy.
However, after each use, you must roll a Constitution saving throw (DC 11) or suffer one level of exhaustion.
\paragraph*{Telekinetic Shove} As a bonus action, you can attempt to shove a medium-sized or smaller creature within 15 feet of you
using telekinesis.
The target must succeed on a Strength saving throw (DC 8 plus the spellcasting ability modifier) or be pushed 5 feet away from you.
Optionally, you can choose to pull the target 5 feet closer to you instead.
\paragraph*{Feather Fall} You can cast \emph{Feather Fall} on yourself or a creature you can see within 60 feet of you at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 11) or suffer one level of exhaustion.

\subsection{Telekinesis II}
{\emph{General Feat (Prerequisite: Telekinesis I)}}\par
\paragraph*{Levitate} You can cast \emph{Levitate} on yourself or one creature within 60 feet of youat will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 12) or suffer one level of exhaustion.
Note that you can lift creatures and stop the levitation at will.
The creature takes damage as per rules if it is dropped from a height, and is prone after the fall.
\paragraph*{Telekinetic Strike} As an action, you can hurl a small or tiny object within 30 feet of you
using telekinesis. Make a ranged spell attack (spellcasting ability modifier + proficiency bonus to hit).
On a hit, the target takes $ 1d6 $ bludgeoning damage, or $ 1d4 $ if the object is tiny.
You can get the object back to you as a bonus action.
\paragraph*{Telekinetic Shove} As per above, but the size is increased to large.
The maximum weight that you can pull or push this way is 500 pounds.
\paragraph*{Gust of Wind} You can cast \emph{Gust of Wind} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 12) or suffer one level of exhaustion.
This effect is slightly different than the spell version:
The effect is not a wind but telekinetic force acting on objects and creatures.
As such, it does not disperse gas or vapor effects, nor does it extinguish candles, torches, or similar unprotected flames.

\subsection{Telekinesis III}
{\emph{General Feat (Prerequisite: Telekinesis II)}}\par
\paragraph*{Ability Score Increase} Increase either your Constitution or your spellcasting ability score by 1, to a maximum of 20.
\paragraph*{Fly} You can cast \emph{Fly} on yourself or one creature that you can touch at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 13) or suffer one level of exhaustion.
\paragraph*{Telekinetic Shove} As per above, but the size is increased to huge.
There is no weight limit for this ability.

\subsection{Telekinesis IV}
{\emph{General Feat (Prerequisite: Telekinesis III)}}\par
\paragraph*{Bigby's Hand} You can cast \emph{Bigby's Hand} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 15) or suffer one level of exhaustion.
The hand is invisible, and cannot be detected by mundane means,
although \emph{Detect Magic} and similar magical means reveals it.
If detected through \emph{True Seeing}, it does not appear as a normal hand, but rather a mass of telekinetic energy.
\paragraph*{Blade Barrier} You can cast \emph{Blade Barrier} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 16) or suffer one level of exhaustion.
The blades are invisible, and cannot be detected by mundane means,
although \emph{Detect Magic} and similar magical means reveals them.
If detected through \emph{True Seeing}, they do not appear as normal blades, but rather slivers and blades of telekinetic energy.
They still provider cover as per the spell, since they are moving rapidly enough to provide that effect.
\paragraph*{Disintegrate} You can cast \emph{Disintegrate} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 16) or suffer one level of exhaustion.
\paragraph*{Telekinesis} You can cast \emph{Telekinesis} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 15) or suffer one level of exhaustion.
\paragraph*{Wall of Force} You can cast \emph{Wall of Force} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 15) or suffer one level of exhaustion.

\subsection{Telekinesis V}
{\emph{General Feat (Prerequisite: Telekinesis IV)}}\par
\paragraph*{Ability Score Increase} Increase either your Constitution or your spellcasting ability score by 1, to a maximum of 20.
\paragraph*{Telekinetic Shove} As per above, but the size is increased to gargantuan.
\paragraph*{Mordenkainen's Sword} You can cast \emph{Mordenkainen's Sword} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 17) or suffer one level of exhaustion.
The sword is invisible, and cannot be detected by mundane means,
although \emph{Detect Magic} and similar magical means reveals it.
If detected through \emph{True Seeing}, it does not appear as a normal sword, but rather a mass of telekinetic energy.

\subsection{Boon of Telekinesis}
{\emph{Epic Boon Feat (Prerequisite: Telekinesis V)}}\par
You have achieved a pinnacle of telekinetic ability.
\paragraph*{Ability Score Increase} Increase either your Constitution or your spellcasting ability score by 1, to a maximum of 30.
\paragraph*{Telekinetic Mastery}
You can cast \emph{Telekinesis} at will, without requiring verbal or somatic components. This does not require a Constitution saving throw.
Simiarly, \emph{Fly}

\section*{Telepathy}

\subsection{Telepathy I}
{\emph{Origin Feat}}\par
Whether by mutation, training, or some other means, you have learned to communicate mentally with others.
You gain the following abilities:
\paragraph*{Friends} You gain the \emph{Friends} cantrip,
except it does not require verbal or somatic components.
Your spellcasting ability for this cantrip is Charisma or Wisdom - discuss with the DM.
\paragraph*{Charm Person} You can cast \emph{Charm Person} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 11) or suffer one level of exhaustion.
\paragraph*{Command} You can cast \emph{Command} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 11) or suffer one level of exhaustion.
\paragraph*{Zone of Truth} You can cast \emph{Zone of Truth} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 11) or suffer one level of exhaustion.

\subsection{Telepathy II}
{\emph{General Feat (Prerequisite: Telepathy I)}}\par
\paragraph*{Detect Thoughts} You can cast \emph{Detect Thoughts} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 12) or suffer one level of exhaustion.
\paragraph*{Hold Person} You can cast \emph{Hold Person} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 12) or suffer one level of exhaustion.
\paragraph*{Suggestion} You can cast \emph{Suggestion} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 12) or suffer one level of exhaustion.

\subsection{Telepathy III}
{\emph{General Feat (Prerequisite: Telepathy II)}}\par
\paragraph*{Ability Score Increase} Increase either your Constitution or your spellcasting ability score by 1, to a maximum of 20.
\paragraph*{Sending} You can cast \emph{Sending} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 13) or suffer one level of exhaustion.
\paragraph*{Compulsion} You can cast \emph{Compulsion} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 14) or suffer one level of exhaustion.
\paragraph*{Charm Monster} You can cast \emph{Charm Monster} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 14) or suffer one level of exhaustion.
\paragraph*{Locate Creature} You can cast \emph{Locate Creature} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 14) or suffer one level of exhaustion.

\subsection{Telepathy IV}
{\emph{General Feat (Prerequisite: Telepathy III)}\par
\paragraph*{Mass Suggestion} You can cast \emph{Mass Suggestion} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 16) or suffer one level of exhaustion.
\paragraph*{Dominate Person} You can cast \emph{Dominate Person} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 15) or suffer one level of exhaustion.
\paragraph*{Dream} You can cast \emph{Dream} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 15) or suffer one level of exhaustion.
\paragraph*{Rary's Telepathic Bond} You can cast \emph{Rary's Telepathic Bond} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 15) or suffer one level of exhaustion.

\subsection{Telepathy V}
{\emph{General Feat (Prerequisite: Telepathy IV)}}\par
\paragraph*{Ability Score Increase} Increase either your Constitution or your spellcasting ability score by 1, to a maximum of 20.
\paragraph*{Dominate Monster} You can cast \emph{Dominate Monster} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 18) or suffer one level of exhaustion.
\paragraph*{Glibness} You can cast \emph{Glibness} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 18) or suffer one level of exhaustion.
\paragraph*{Power Word Stun} You can cast \emph{Power Word Stun} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 18) or suffer one level of exhaustion.
\paragraph*{Telepathy} You can cast \emph{Telepathy} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 18) or suffer one level of exhaustion.


\subsection{Boon of Telepathy}
{\emph{Epic Boon Feat (Prerequisite: Telepathy V)}}\par
You have achieved a pinnacle of telepathic ability.
\paragraph*{Ability Score Increase} Increase either your Constitution or your spellcasting ability score by 1, to a maximum of 30.
\paragraph*{Telepathic Communication}
You can communicate telepathically with any creature you can see within 1 mile of you.
You can also cast \emph{Rary's Telepathic Bond}, \emph{Telepathy}, \emph{Sending} at will,
without requiring verbal or somatic components. This does not require a Constitution saving throw.
\paragraph*{Power Word Kill} You can cast \emph{Power Word Kill} at will,
without requiring verbal or somatic components. However, after each use, you must roll a Constitution saving throw (DC 19) or suffer one level of exhaustion.



\end{document}
